Pillar 1 - Sequential Pattern Mining

### 2019-01-30 Pillar 1 - Sequential Pattern Mining.Rmd
Save AR for App

    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_")
    ) %>%
  rename(
    item = `Course ID`
  )
```
### Adding not taken courses
```{r}
d_transactions_tmp <- expand.grid(sequenceID = unique(d_transactions$sequenceID),item = unique(d_transactions$item)) %>%
  left_join(d_transactions, by = c("sequenceID","item")) %>%
  mutate(
    Taken= case_when(
     is.na(Grade)  ~ "not taken",
      T             ~ "taken"),
    item_Taken= paste(item,Taken, sep = "_")
     )

@@

#
# Save association rules
save(AR, AR_PF, AR_HL, AR_Taken,
     file = "Output/AS.RDATA")

# TODO: MAKE APP

>>>>

    item_PF = paste(`Course ID`, PF, sep = "_"),
    item_HL = paste(`Course ID`, HL, sep = "_")
    ) %>%
  rename(
    item = `Course ID`
  )
```

### Adding not taken courses
```{r}
d_transactions_tmp <- expand.grid(sequenceID = unique(d_transactions$sequenceID),item = unique(d_transactions$item)) %>%
  left_join(d_transactions, by = c("sequenceID","item")) %>%
  mutate(
    Taken= case_when(
     is.na(Grade)  ~ "not taken",
      T             ~ "taken"),
    item_Taken= paste(item,Taken, sep = "_")
     )

@@

#
# Save association rules
AR <- list(
    AR = AR,
    AR_PF = AR_PF,
    AR_HL = AR_HL,
    AR_Taken = AR_Taken
    )

save(AR, file = "App/AR.RDATA")
